\chapter{Conclusion}
In the final chapter of this thesis, the findings and results from the previous chapters are summarized. 
Additionally, an outlook on the future improvements of the system is discussed, identifying areas for further development and research. 

\section{Summary}
In conclusion, the aim of this project was to develop an application that allows users to monitor their health using a Bluetooth Low Energy connection, while also improving user control over their data. 
The application was implemented by using BLE connection to stream real-time heart rate data, providing users with accurate information regarding their cardiovascular activity. 
Additionally, user management features were implemented to ensure users have full control over their personal data.
As the result of this thesis, the application fulfills the user stories described in \autoref{chap:user_stories}.
Users can conveniently track their heart rate, monitor their current activity, stay informed of their energy expenditure during an exercise, and manage their data including deleting all of their data. 
The implementation of features such as heart rate streaming and exercise tracking has provided valuable functionality to users.

\section{Outlook}
Looking ahead, there are several areas for future improvement. 
Firstly, the application currently uses an outdated formula, which may not provide the most precise estimation of calories burned during exercises. 
Updating the formula with more recent research could improve the accuracy of this feature.
Moreover, the visual representation of the heart rate graph could be enhanced by including time information to provide more context.
Additionally, it would be beneficial to thoroughly test and validate the compatibility of the application with other heart rate sensors, in addition to the currently supported Polar heart rate sensors. 
This will ensure that a wider range of users can benefit from the app and use their preferred heart rate sensors for health monitoring.