
\begin{longtable}{p{0.2\textwidth} p{0.1\textwidth} p{0.5\textwidth} p{0.2\textwidth}}
    \label{tab:qualitystandard}\\

    \caption{Core application quality standard based on Android Documentation \autocite{androidqualityguidelines} and its relevance}\\

        \hline
        \textbf{Area} & \textbf{ID} & \textbf{Description} & \textbf{Relevance} \\
        \hline
        Navigation & VX-N1 & The app supports standard Back button navigation and does not make use of any custom, on-screen "Back button" prompts. & less important \\
         & VX-N2 & The app supports gesture navigation for going back / going to the home screen. & less important \\
         & VX-N3 & The app correctly preserves and restores user or app state. & important \\
  
        UI and Graphics & VX-U1 & The app supports both landscape and portrait orientations (if possible) and folding / unfolding. & less important \\
         & VX-U3 & The app correctly handles rapid transitions between display orientations and device folding / unfolding without rendering problems or losing state. & less important \\
  
        Visual quality & VX-V1 & The app displays graphics, text, images, and other UI elements without noticeable distortion, blurring, or pixelation. The app should use vector drawables where possible. & less important \\
         & VX-V3 & The app's content, and all web contents referred to by the app, support dark theme. & not important \\
        
        Accessibility & VX-A1 & Touch targets should be at least 48dp in size. & less important \\
         & VX-A2 & The app's text and foreground content should maintain a high enough color contrast ratio with its background. & important \\
  
        Background Service & FN-B1 & The app avoids running unnecessarily long services in the background. To ensure the smooth running of the user's device, the system applies various restrictions on background services. & important\\

        Stability & PS-S1 & The app does not crash or block the UI thread causing ANR ("Android Not Responding") errors.  & very important\\

        Performance & PS-P1 & The app loads quickly or provides onscreen feedback to the user (a progress indicator or similar cue) if the app takes longer than two seconds to load. & important\\
        
        Permissions & SC-P1 & The app requests only the absolute minimum number of permissions that it needs to support its use case at hand. & important \\
        & SC-P4 & The app clearly conveys why certain permissions are needed or follows the recommended flow to explain why it needs a permission. &  important \\
        & SC-P5 & The app should gracefully degrade when users deny or revoke a permission. The app should not prevent the user from accessing the app altogether. & important\\
        
        Data \& Files & SC-DF1 & All sensitive data is stored in the app's internal storage. & important\\
         & SC-DF2 & No personal or sensitive user data is logged to the system log or an app-specific log. & important\\
         & SC-DF3 & The app does not use any non-resettable hardware IDs, such as the IMEI, for identification purposes. & not important\\

        
        \hline
\end{longtable}

