\chapter{Requirement Analysis}
This chapter includes analysis of the requirements of the system based on the problem statement described in the previous chapter. Furthermore, the main goal of the software as well as other specifications will be analyzed.

\section{Goal}
The goal of this research project is to build a functional prototype of a mobile application that monitors users' health and activity by observing users' heart rate. To observe one's heart rate, the application will be establish connection to a heart rate sensor via bluetooth low energy.
With the help of bluetooth low energy connection, the sensor is able to broadcast heart rate data to the application while consuming minimal energy.
The retrieved data will be stored in local database instead of cloud services or wearable devices to ensure data privacy. The user will also be given full control over their data, allowing them to modify or delete their data according to their will at anytime.
The retrieved data can be accessed later for visualization purposes as long as it is available. Furthermore, the application should be able to calculate users' energy expenditure during their exercise based on their heart rate, age, gender, weight, duration of exercise.

\section{State of the Art}
Health monitoring using wearable devices has gained immense popularity, enabling individuals to conveniently monitor their health and fitness. Bluetooth low energy (BLE) plays an important role in establishing connection between wearable device, which acts as a sensor, and the application. 
BLE offers real-time data exchange while consuming low power, which allows for long-term deployment without the need of frequent battery change. \cite{strey2013ble}
Existing health and activity monitor applications utilizing BLE offer a range of features and functionalities such as heart rate, calories burned, sleep patterns.

Nevertheless, as mentioned earlier, the challenges remain in maintaining a straightforward application and ensuring users' privacy. The aim in this research project is to explore the possibilities of improving health and wellbeing of the user by providing real-time data on their heart rate while providing users full control over their own data.
By addressing these challenges, this research project intends to develop a prototype of a more user- and privacy-friendly health activity monitor application using BLE.
\newpage

\section{Requirements}
In this chapter, the requirements of the application is listed by identifying and analyzing the use cases from the research project's goals and priorities.

\subsection{Use Cases}
Use Cases section

\subsection{User Stories}
User Stories section

\subsection{Software Quality Standard}
Software Quality section